Capabilities, MMIO and Robust Safety

### 2020-04-14 capability-notes/driver-notes/main.tex
driver notes: bootCont_sem: get rid of the InitW predicate
cosmetic tweak

\begin{align*}
    \X{state\_interp} \; (r,m,t) :=& \X{gen\_heap\_ctx}\; r \ast\\
    &\X{gen\_heap\_ctx}\; m \ast \dom(m) \cap \MMIO = \emptyset \ast
    {\color{BrickRed}\tracefull{t}}
\end{align*}

@@

 \X{InitW}(\Winit,b,e) \eqdef\\
\quad \text{Predicate that forces  $\Winit$ to be the world with one
    permanent, standard region at $[b,e[$}\\[0.8em]

 \X{bootCont_{sem}}(P, g, b, e, A_{\X{entry}},\Phi,\Winit) \eqdef  \\[0.2em]
    \begin{array}{l}
       (\exists b_{\X{adv}}\; e_{\X{adv}}.\; \\[0.5em]
      \quad
      \begin{array}{l}
        \X{InitW}(\Winit,b_{\X{adv}}, e_{\X{adv}})\ast \\[0.5em]
        \X{PC} \mapsto_{r} (\X{RWX}, \X{G}, b_{\X{PC}}, e_{\X{PC}}, a_{\X{PC}})
        \ast \VR^{\notMMIO} (\Winit)(\X{RW}, \X{G}, b_{\X{PC}}, e_{\X{PC}}, a_{\X{PC}})) \ast {} \\[1.2em]
        \bigast{r \in Reg\setminus \{\X{PC}\}}{(r \mapsto_{r} w_r \ast
        \VR^{\notMMIO} (\Winit)(w_r))} \ast {} \\[1.2em]
        \driverC(b,e,\overline{\V{w}_l})\ast
        \; \trInv \; \ast \\[0.5em]
        \X{region}(\Winit) \ast  \X{sts\_full\_world}\; \X{sts\_std} \;
        \Winit)\\[0.5em]       \end{array}
    \end{array} \\[4em]
    \quad\wand
    \begin{array}{l}
     \wpre{\I{Seq}\; (\I{Instr}\; \I{Executable})}{\Phi}
    \end{array}\\[1.2em]

>>>>

\begin{align*}
    \X{state\_interp} \; (r,m,t) := {} & \X{gen\_heap\_ctx}\; r \ast {}\\
    &\X{gen\_heap\_ctx}\; m \ast \dom(m) \cap \MMIO = \emptyset \ast
    {\color{BrickRed}\tracefull{t}}
\end{align*}

@@

 \X{bootCont_{sem}}(P, g, b, e, A_{\X{entry}},\Phi,\Winit) \eqdef  \\[0.2em]
    \begin{array}{l}
       (\exists b_{\X{adv}}\; e_{\X{adv}}\; a_{\X{adv}}\; w_r.\; \\[0.5em]
      \quad
      \begin{array}{l}
        \X{PC} \mapsto_{r} (\X{RWX}, \X{G}, b_{\X{adv}}, e_{\X{adv}}, a_{\X{adv}})
        \ast \VR^{\notMMIO} (\Winit)(\X{RW}, \X{G}, b_{\X{adv}}, e_{\X{adv}}, a_{\X{adv}})) \ast {} \\[1.2em]
        \bigast{r \in Reg\setminus \{\X{PC}\}}{(r \mapsto_{r} w_r \ast
        \VR^{\notMMIO} (\Winit)(w_r))} \ast {} \\[1.2em]
        \driverC(b,e,\overline{\V{w}_l})\ast
        \; \trInv \; \ast \\[0.5em]
        \X{region}(\Winit) \ast  \X{sts\_full\_world}\; \X{sts\_std} \;
        \Winit)\\[0.5em]       \end{array}
    \end{array} \\[4em]
    \quad\wand
    \begin{array}{l}
     \wpre{\I{Seq}\; (\I{Instr}\; \I{Executable})}{\Phi}
    \end{array}\\[1.2em]
